### 2022-05-03 src/paper.tex
Update

% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Remove the "review" option to generate the final version.
\usepackage[]{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{Finding ARG1 of Partitive Nouns in NomBank with DistilBERT}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

\author{Ziyang Zeng \\
  Dept. of Computer Science \\
  New York University \\
  \texttt{zz2960@nyu.edu}}

\begin{document}
\maketitle
\begin{abstract}
  This document is a supplement to the general instructions for *ACL authors. It contains instructions for using the \LaTeX{} style files for ACL conferences.
  The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
  These instructions should be used both for papers submitted for review and for final versions of accepted papers.
\end{abstract}

\section{Introduction}

NomBank (Meyers et al., 2004c) is a databank project at New York University that adds annotation layer of argument structure for instances in the Penn Treebank II corpus. Apart from the more commonly researched nominalizations of verbs and nominalizations of adjectives, it also covers relational nouns, partitive nouns and several other types of types of argument-taking nouns.

BERT (Devlin et al., 2018) is a large-size language representation model trained on a large corpus of English text that can achieve state-of-the-art results on a variety of natural language processing tasks. BERT came a decade later than the release of NomBank and there's been little previous work in using it to conduct NomBank-based tasks and related experiments. However, as powerful as BERT is, its large parameters size makes it significantly more computationally expensive to train and use. On the other hand, DistilBERT is a distilled student model of BERT that retains 97\% of BERT's language understanding capabilities while being 40\% smaller and 60\% faster.

This paper presents a token classification approach using pre-trained DistilBERT to find ARG1 of partitive nouns in NomBank. It focuses on partitive nouns (nouns that are used to describe a part or quantity of something) and the partitive task. The task is described as finding one argument (ARG1) of \% (the percent sign), or in other words, finding the none group that is being sub-divided or quantified over. For example, for the sentence "Output in the energy sector rose 3.8\%.", the ARG1 to be found is "Output" since it is the partitive noun that "3.8\%" is referring to. This task can be translated into a binary classification problem on each token in the sentence where the model predicts whether the token is an ARG1 or not.

In addition to the token classification approach above, this paper also experiments with question-answer task, transforming the original ARG1 finding task into the task of make the model answer the question "What is the ARG1 of this sentence?". The advantage of this adaptation is that the model would stably output exactly one ARG1 for each sentence whereas token classification could give each sentence 0 to N ARG1s.

\section{Engines}

To produce a PDF file, pdf\LaTeX{} is strongly recommended (over original \LaTeX{} plus dvips+ps2pdf or dvipdf). Xe\LaTeX{} also produces PDF files, and is especially suitable for text in non-Latin scripts.

\section{Preamble}

The first line of the file must be
\begin{quote}
  \begin{verbatim}
\documentclass[11pt]{article}
\end{verbatim}
\end{quote}

To load the style file in the review version:
\begin{quote}
  \begin{verbatim}
\usepackage[review]{acl}
\end{verbatim}
\end{quote}
For the final version, omit the \verb|review| option:
\begin{quote}
  \begin{verbatim}
\usepackage{acl}
\end{verbatim}
\end{quote}

To use Times Roman, put the following in the preamble:
\begin{quote}
  \begin{verbatim}
\usepackage{times}
\end{verbatim}
\end{quote}
(Alternatives like txfonts or newtx are also acceptable.)

Please see the \LaTeX{} source of this document for comments on other packages that may be useful.

Set the title and author using \verb|\title| and \verb|\author|. Within the author list, format multiple authors using \verb|\and| and \verb|\And| and \verb|\AND|; please see the \LaTeX{} source for examples.

By default, the box containing the title and author names is set to the minimum of 5 cm. If you need more space, include the following in the preamble:
\begin{quote}
  \begin{verbatim}
\setlength\titlebox{<dim>}
\end{verbatim}
\end{quote}
where \verb|<dim>| is replaced with a length. Do not set this length smaller than 5 cm.

\section{Document Body}

\subsection{Footnotes}

Footnotes are inserted with the \verb|\footnote| command.\footnote{This is a footnote.}

\subsection{Tables and figures}

See Table~\ref{tab:accents} for an example of a table and its caption.
\textbf{Do not override the default caption sizes.}

\begin{table}
  \centering
  \begin{tabular}{lc}
    \hline
    \textbf{Command} & \textbf{Output} \\
    \hline
    \verb|{\"a}|     & {\"a}           \\
    \verb|{\^e}|     & {\^e}           \\
    \verb|{\`i}|     & {\`i}           \\
    \verb|{\.I}|     & {\.I}           \\
    \verb|{\o}|      & {\o}            \\
    \verb|{\'u}|     & {\'u}           \\
    \verb|{\aa}|     & {\aa}           \\\hline
  \end{tabular}
  \begin{tabular}{lc}
    \hline
    \textbf{Command} & \textbf{Output} \\
    \hline
    \verb|{\c c}|    & {\c c}          \\
    \verb|{\u g}|    & {\u g}          \\
    \verb|{\l}|      & {\l}            \\
    \verb|{\~n}|     & {\~n}           \\
    \verb|{\H o}|    & {\H o}          \\
    \verb|{\v r}|    & {\v r}          \\
    \verb|{\ss}|     & {\ss}           \\
    \hline
  \end{tabular}
  \caption{Example commands for accented characters, to be used in, \emph{e.g.}, Bib\TeX{} entries.}
  \label{tab:accents}
\end{table}

\subsection{Hyperlinks}

Users of older versions of \LaTeX{} may encounter the following error during compilation:
\begin{quote}
  \tt\verb|\pdfendlink| ended up in different nesting level than \verb|\pdfstartlink|.
\end{quote}
This happens when pdf\LaTeX{} is used and a citation splits across a page boundary. The best way to fix this is to upgrade \LaTeX{} to 2018-12-01 or later.

\subsection{Citations}

\begin{table*}
  \centering
  \begin{tabular}{lll}
    \hline
    \textbf{Output}           & \textbf{natbib command} & \textbf{Old ACL-style command} \\
    \hline
    \citep{Gusfield:97}       & \verb|\citep|           & \verb|\cite|                   \\
    \citealp{Gusfield:97}     & \verb|\citealp|         & no equivalent                  \\
    \citet{Gusfield:97}       & \verb|\citet|           & \verb|\newcite|                \\
    \citeyearpar{Gusfield:97} & \verb|\citeyearpar|     & \verb|\shortcite|              \\
    \hline
  \end{tabular}
  \caption{\label{citation-guide}
    Citation commands supported by the style file.
    The style is based on the natbib package and supports all natbib citation commands.
    It also supports commands defined in previous ACL style files for compatibility.
  }
\end{table*}

Table~\ref{citation-guide} shows the syntax supported by the style files.
We encourage you to use the natbib styles.
You can use the command \verb|\citet| (cite in text) to get ``author (year)'' citations, like this citation to a paper by \citet{Gusfield:97}.
You can use the command \verb|\citep| (cite in parentheses) to get ``(author, year)'' citations \citep{Gusfield:97}.
You can use the command \verb|\citealp| (alternative cite without parentheses) to get ``author, year'' citations, which is useful for using citations within parentheses (e.g. \citealp{Gusfield:97}).

\subsection{References}

\nocite{Ando2005,borschinger-johnson-2011-particle,andrew2007scalable,rasooli-tetrault-2015,goodman-etal-2016-noise,harper-2014-learning}

The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
If your own bib file is named \texttt{custom.bib}, then placing the following before any appendices in your \LaTeX{} file will generate the references section for you:
\begin{quote}
  \begin{verbatim}
\bibliographystyle{acl_natbib}
\bibliography{custom}
\end{verbatim}
\end{quote}

You can obtain the complete ACL Anthology as a Bib\TeX{} file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
To include both the Anthology and your own .bib file, use the following instead of the above.
\begin{quote}
  \begin{verbatim}
\bibliographystyle{acl_natbib}
\bibliography{anthology,custom}
\end{verbatim}
\end{quote}

Please see Section~\ref{sec:bibtex} for information on preparing Bib\TeX{} files.

\subsection{Appendices}

Use \verb|\appendix| before any appendix section to switch the section numbering over to letters. See Appendix~\ref{sec:appendix} for an example.

\section{Bib\TeX{} Files}
\label{sec:bibtex}

Unicode cannot be used in Bib\TeX{} entries, and some ways of typing special characters can disrupt Bib\TeX's alphabetization. The recommended way of typing special characters is shown in Table~\ref{tab:accents}.

Please ensure that Bib\TeX{} records contain DOIs or URLs when possible, and for all the ACL materials that you reference.
Use the \verb|doi| field for DOIs and the \verb|url| field for URLs.
If a Bib\TeX{} entry has a URL or DOI field, the paper title in the references section will appear as a hyperlink to the paper, using the hyperref \LaTeX{} package.

\section*{Acknowledgements}

This document has been adapted
by Steven Bethard, Ryan Cotterell and Rui Yan
from the instructions for earlier ACL and NAACL proceedings, including those for
ACL 2019 by Douwe Kiela and Ivan Vuli\'{c},
NAACL 2019 by Stephanie Lukin and Alla Roskovskaya,
ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu,
NAACL 2018 by Margaret Mitchell and Stephanie Lukin,
Bib\TeX{} suggestions for (NA)ACL 2017/2018 from Jason Eisner,
ACL 2017 by Dan Gildea and Min-Yen Kan,
NAACL 2017 by Margaret Mitchell,
ACL 2012 by Maggie Li and Michael White,
ACL 2010 by Jing-Shin Chang and Philipp Koehn,
ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui,
ACL 2005 by Hwee Tou Ng and Kemal Oflazer,
ACL 2002 by Eugene Charniak and Dekang Lin,
and earlier ACL and EACL formats written by several people, including
John Chen, Henry S. Thompson and Donald Walker.
Additional elements were taken from the formatting instructions of the \emph{International Joint Conference on Artificial Intelligence} and the \emph{Conference on Computer Vision and Pattern Recognition}.

% Entries for the entire Anthology, followed by custom entries
\bibliography{anthology,custom}
\bibliographystyle{acl_natbib}

\appendix

\section{Example Appendix}
\label{sec:appendix}

This is an appendix.

\end{document}

### 2022-05-03 src/paper.tex
Update

@@
 NomBank (Meyers et al., 2004c) is a databank project at New York University that adds annotation layer of argument structure for instances in the Penn Treebank II corpus.
-Apart from the more commonly researched nominalizations of verbs and nominalizations of adjectives, it also covers relational nouns, partitive nouns and several other types of types of argument-taking nouns.
+Apart from the more commonly researched nominalizations of verbs and nominalizations of adjectives, it also covers relational nouns, partitive nouns and several other types of argument-taking nouns.
 
@@
 
-\section{Engines}
+\section{Related Work}
 
-To produce a PDF file, pdf\LaTeX{} is strongly recommended (over original \LaTeX{} plus dvips+ps2pdf or dvipdf).
-Xe\LaTeX{} also produces PDF files, and is especially suitable for text in non-Latin scripts.
+NomBank (Meyers et al., 2004c), as a databank extending the frames of NOMLEX and PropBank, annotates argument structures of common nouns similar to how PropBank annotates predicating verbs.
+The development of the NomBank corpus has supported the work of (Jiang and Ng, 2006) and (Liu and Ng, 2007).
+Each study tested the hypothesis that machine learning methodologies and representations used in verbal SRL (cf.
+(Pradhan et al., 2005)) can be ported to the task of NomBank SRL.
+(Liu and Ng, 2007) reports an overall f-measure score of 0.7283 using automatically generated parse trees, demonstrating that modest performance can be achieved using basic approaches developed in the verbal domain.
+Both studies also investigated the use of features specific to the task of nominal SRL, but observed only marginal performance gains.
 

### 2022-05-03 src/paper.tex
Update

@@
   New York University \\
+  251 Mercer Street, New York, NY \\
   \texttt{zz2960@nyu.edu}}
@@
 BERT (Devlin et al., 2018) is a large-size language representation model trained on a large corpus of English text that can achieve state-of-the-art results on a variety of natural language processing tasks.
-BERT came a decade later than the release of NomBank and there's been little previous work in using it to conduct NomBank-based tasks and related experiments.
+BERT came a decade later than the release of NomBank and there's been little previous work using it to conduct NomBank-based tasks and related experiments.
 However, as powerful as BERT is, its large parameters size makes it significantly more computationally expensive to train and use.
 On the other hand, DistilBERT is a distilled student model of BERT that retains 97\% of BERT's language understanding capabilities while being 40\% smaller and 60\% faster.
+This makes it a great candidate to train when facing with limited resources.
 
@@
 NomBank (Meyers et al., 2004c), as a databank extending the frames of NOMLEX and PropBank, annotates argument structures of common nouns similar to how PropBank annotates predicating verbs.
-The development of the NomBank corpus has supported the work of (Jiang and Ng, 2006) and (Liu and Ng, 2007).
-Each study tested the hypothesis that machine learning methodologies and representations used in verbal SRL (cf.
-(Pradhan et al., 2005)) can be ported to the task of NomBank SRL.
-(Liu and Ng, 2007) reports an overall f-measure score of 0.7283 using automatically generated parse trees, demonstrating that modest performance can be achieved using basic approaches developed in the verbal domain.
-Both studies also investigated the use of features specific to the task of nominal SRL, but observed only marginal performance gains.
+The development of the NomBank corpus has made several other work on argument structure extraction more accessible.
+Jiang and Ng (2006) attempts the first NomBank-based automatic semantic role labeling system after the databank's release.
+Ping (2006)  adapts a PropBank-based SRL system to the SRL task of NomBank, achieving an overall F1 score of 72.73 on section 23 of the NomBank corpus.
+
+More recently, the NLP community has seen huge popularity in heavily adopting pretraining-based langauge models.
+The latest development on this is transformers-based models including BERT.
+BERT, or Bidirectional Encoder Representations from Transformers (Devlin et al., 2018), is a pretrained language model that can achieve state-of-the-art results on a variety of natural language processing tasks.
 

### 2022-05-03 src/paper.tex
Update

@@
 
+More recently, the NLP community has seen huge popularity in heavily adopting pretraining-based langauge models.
 BERT (Devlin et al., 2018) is a large-size language representation model trained on a large corpus of English text that can achieve state-of-the-art results on a variety of natural language processing tasks.
@@
 
-More recently, the NLP community has seen huge popularity in heavily adopting pretraining-based langauge models.
-The latest development on this is transformers-based models including BERT.
-BERT, or Bidirectional Encoder Representations from Transformers (Devlin et al., 2018), is a pretrained language model that can achieve state-of-the-art results on a variety of natural language processing tasks.
+BERT, or Bidirectional Encoder Representations from Transformers (Devlin et al., 2018), has shown state-of-the-art results on many NLP tasks.
+There have been many attempts to compress BERT into a smaller model, among which DistilBERT (Sanh et al., 2019) successfully reduces the size of a BERT model by 40\%, while retaining 97\% of its language understanding capabilities and being 60\% faster, leveraging  knowledge distillation (Bucila et al., 2006, Hinton et al., 2015) during the pre-training phase.
 

### 2022-05-04 src/paper.tex
Update

@@
 \usepackage{latexsym}
+\usepackage{float}
+\usepackage{graphicx}
 
@@
 
-\section{Preamble}
+More recent development on semantic role labeling (SRL) has shifted from feature engineering to architecture-based modeling leveraging deep neural networks (Collobert
+et al., 2011).
+Several recent notable approaches suggest only using raw tokenized text as input and let the model learn the features from the text itself (He et al., 2017; Sahin and Steedman, 2018; Marcheggiani et al., 2017; Strubell et al., 2018).
+This end-to-end approach allows the model to easily generalize from one SRL task to another without very task-specific feature engineering effort.
 
-The first line of the file must be
-\begin{quote}
-  \begin{verbatim}
-\documentclass[11pt]{article}
-\end{verbatim}
-\end{quote}
+\section{ARG1 Finding Pipelines}
 
-To load the style file in the review version:
-\begin{quote}
-  \begin{verbatim}
-\usepackage[review]{acl}
-\end{verbatim}
-\end{quote}
-For the final version, omit the \verb|review| option:
-\begin{quote}
-  \begin{verbatim}
-\usepackage{acl}
-\end{verbatim}
-\end{quote}
+\subsection{Maximum Entropy Baseline Pipeline}
 
-To use Times Roman, put the following in the preamble:
-\begin{quote}
-  \begin{verbatim}
-\usepackage{times}
-\end{verbatim}
-\end{quote}
-(Alternatives like txfonts or newtx are also acceptable.)
+The baseline we use is a maximum entropy machine learning method in a token-by-token classification manner.
+Maximum entropy is a general technique for estimating probability distributions from data.
+Labeled training data
+is used to derive a set of constraints for the model that
+characterize the class-specific expectations for the distribution.
+To perform well, the model relies on the good representation of the features we feed it.
+In this paper, we select features including the word stem, the neighboring 2 words, POS tags, NG-BIO tags, whether capitalized and the position of the word in the sentence.
 
-Please see the \LaTeX{} source of this document for comments on other packages that may be useful.
+\subsection{Plain Raw Input Pipeline}
+\label{section:plain-pipeline}
 
-Set the title and author using \verb|\title| and \verb|\author|.
-Within the author list, format multiple authors using \verb|\and| and \verb|\And| and \verb|\AND|; please see the \LaTeX{} source for examples.
+The simplest pipeline for finding ARG1 of partitive nouns in NomBank assumes that the input text is raw and unprocessed.
+The pipeline first tokenizes the text using the tokenizer provided by DistilBERT.
+Then, the model predicts whether each token is an ARG1 or not.
+The pipeline is illustrated in the following figure \ref{fig:simplest-arg1-pipeline}.
 
-By default, the box containing the title and author names is set to the minimum of 5 cm. If you need more space, include the following in the preamble:
-\begin{quote}
-  \begin{verbatim}
-\setlength\titlebox{<dim>}
-\end{verbatim}
-\end{quote}
-where \verb|<dim>| is replaced with a length. Do not set this length smaller than 5 cm.
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{assets/simplest-arg1-pipeline.png}
+  \caption{The simplest pipeline for finding ARG1 of partitive nouns in NomBank}
+  \label{fig:simplest-arg1-pipeline}
+\end{figure}
 
-\section{Document Body}
+\subsection{Feature Enhanced Pipeline}
 
-\subsection{Footnotes}
+NomBank provides a number of features for each token in the databank, including POS tags and NG-BIO tags.
+They could be helpful for the task of finding ARG1 of partitive nouns.
+The pipeline below incorporate these features to the raw text input in \ref{section:plain-pipeline} to find ARG1 of partitive nouns.
+The pipeline is illustrated in the figure \ref{fig:enhanced-arg1-pipeline}.
 
-Footnotes are inserted with the \verb|\footnote| command.\footnote{This is a footnote.}
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{assets/enhanced-arg1-pipeline.png}
+  \caption{The feature-enhanced pipeline for finding ARG1 of partitive nouns in NomBank}
+  \label{fig:enhanced-arg1-pipeline}
+\end{figure}
 
-\subsection{Tables and figures}
+Because the original pre-trained DistilBERT model does not take extra features including POS and NG-BIO tags as input, we have to modified the token classification model and alter the last linear layer, concatenating the original BERT hidden layer output with the extra features, then doing token classification through the linear layer.
 
-See Table~\ref{tab:accents} for an example of a table and its caption.
-\textbf{Do not override the default caption sizes.}
+\subsection{Question-Answer Pipeline}
 
-\begin{table}
+Apart from token classification, we also explored question-answer approach which rephrase the original problem into a QA problem.
+Question-answering, just as the plain token classification approach, assumes tokenized input and no extra features.
+Additionally, question-answering tasks also requires a question prompt and answer location for each sample while training.
+The pipeline is illustrated in the figure \ref{fig:qa-arg1-pipeline}.
+
+\begin{figure}[h]
   \centering
-  \begin{tabular}{lc}
-    \hline
-    \textbf{Command} & \textbf{Output} \\
-    \hline
-    \verb|{\"a}|     & {\"a}           \\
-    \verb|{\^e}|     & {\^e}           \\
-    \verb|{\`i}|     & {\`i}           \\
-    \verb|{\.I}|     & {\.I}           \\
-    \verb|{\o}|      & {\o}            \\
-    \verb|{\'u}|     & {\'u}           \\
-    \verb|{\aa}|     & {\aa}           \\\hline
-  \end{tabular}
-  \begin{tabular}{lc}
-    \hline
-    \textbf{Command} & \textbf{Output} \\
-    \hline
-    \verb|{\c c}|    & {\c c}          \\
-    \verb|{\u g}|    & {\u g}          \\
-    \verb|{\l}|      & {\l}            \\
-    \verb|{\~n}|     & {\~n}           \\
-    \verb|{\H o}|    & {\H o}          \\
-    \verb|{\v r}|    & {\v r}          \\
-    \verb|{\ss}|     & {\ss}           \\
-    \hline
-  \end{tabular}
-  \caption{Example commands for accented characters, to be used in, \emph{e.g.}, Bib\TeX{} entries.}
-  \label{tab:accents}
-\end{table}
+  \includegraphics[width=\linewidth]{assets/qa-arg1-pipeline.png}
+  \caption{The question-answering pipeline for finding ARG1 of partitive nouns in NomBank}
+  \label{fig:qa-arg1-pipeline}
+\end{figure}
 
-\subsection{Hyperlinks}
+The output of the question-answering model is the location (start index and end index) of the predicted answer.
+By locating the token on the original input token list with the start index and end index, we can reconstruct the ARG1 label of the sentence.
 
-Users of older versions of \LaTeX{} may encounter the following error during compilation:
-\begin{quote}
-  \tt\verb|\pdfendlink| ended up in different nesting level than \verb|\pdfstartlink|.
-\end{quote}
-This happens when pdf\LaTeX{} is used and a citation splits across a page boundary. The best way to fix this is to upgrade \LaTeX{} to 2018-12-01 or later.
+\section{Experiments}
 
-\subsection{Citations}
+\subsection{Dataset}
 
-\begin{table*}
+The dataset we use in this task is part of the NomBank that specifically focus on partitive nouns.
+In the dataset is split into training, dev and test set.
+The training set has 2367 sentences or 66186 words, the dev set has 83 sentences or 2225 words, and the test set has 150 sentences or 4276 words.
+Each token in a sentence takes a line in the data file, the line containing the token itself, the POS tag, the NG-BIO tag, the index of the sentence and the index of the token in the sentence.
+The semantic role label is put at the end of each line, if the label is not one of "ARG1", "PRED" and "SUPPORT", then it's omitted.
+Figure \ref{fig:dataset-one-sample} is one sample sentence from the training dataset.
+
+\begin{figure}[h]
   \centering
-  \begin{tabular}{lll}
-    \hline
-    \textbf{Output}           & \textbf{natbib command} & \textbf{Old ACL-style command} \\
-    \hline
-    \citep{Gusfield:97}       & \verb|\citep|           & \verb|\cite|                   \\
-    \citealp{Gusfield:97}     & \verb|\citealp|         & no equivalent                  \\
-    \citet{Gusfield:97}       & \verb|\citet|           & \verb|\newcite|                \\
-    \citeyearpar{Gusfield:97} & \verb|\citeyearpar|     & \verb|\shortcite|              \\
-    \hline
-  \end{tabular}
-  \caption{\label{citation-guide}
-    Citation commands supported by the style file.
-    The style is based on the natbib package and supports all natbib citation commands.
-    It also supports commands defined in previous ACL style files for compatibility.
-  }
-\end{table*}
+  \includegraphics[width=\linewidth]{assets/dataset-one-sample.png}
+  \caption{One sample sentence in the training dataset}
+  \label{fig:dataset-one-sample}
+\end{figure}
 
-Table~\ref{citation-guide} shows the syntax supported by the style files.
-We encourage you to use the natbib styles.
-You can use the command \verb|\citet| (cite in text) to get ``author (year)'' citations, like this citation to a paper by \citet{Gusfield:97}.
-You can use the command \verb|\citep| (cite in parentheses) to get ``(author, year)'' citations \citep{Gusfield:97}.
-You can use the command \verb|\citealp| (alternative cite without parentheses) to get ``author, year'' citations, which is useful for using citations within parentheses (e.g. \citealp{Gusfield:97}).
-
-\subsection{References}
-
-\nocite{Ando2005,borschinger-johnson-2011-particle,andrew2007scalable,rasooli-tetrault-2015,goodman-etal-2016-noise,harper-2014-learning}
-
-The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
-If your own bib file is named \texttt{custom.bib}, then placing the following before any appendices in your \LaTeX{} file will generate the references section for you:
-\begin{quote}
-  \begin{verbatim}
-\bibliographystyle{acl_natbib}
-\bibliography{custom}
-\end{verbatim}
-\end{quote}
-
-You can obtain the complete ACL Anthology as a Bib\TeX{} file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
-To include both the Anthology and your own .bib file, use the following instead of the above.
-\begin{quote}
-  \begin{verbatim}
-\bibliographystyle{acl_natbib}
-\bibliography{anthology,custom}
-\end{verbatim}
-\end{quote}
-
-Please see Section~\ref{sec:bibtex} for information on preparing Bib\TeX{} files.
-
-\subsection{Appendices}
-
-Use \verb|\appendix| before any appendix section to switch the section numbering over to letters. See Appendix~\ref{sec:appendix} for an example.
-
-\section{Bib\TeX{} Files}
-\label{sec:bibtex}
-
-Unicode cannot be used in Bib\TeX{} entries, and some ways of typing special characters can disrupt Bib\TeX's alphabetization.
-The recommended way of typing special characters is shown in Table~\ref{tab:accents}.
-
-Please ensure that Bib\TeX{} records contain DOIs or URLs when possible, and for all the ACL materials that you reference.
-Use the \verb|doi| field for DOIs and the \verb|url| field for URLs.
-If a Bib\TeX{} entry has a URL or DOI field, the paper title in the references section will appear as a hyperlink to the paper, using the hyperref \LaTeX{} package.
+In a sentence in the \% dataset, the PRED labels \% symbol, the ARG1 is the partitive noun that \% symbol refers to, and the SUPPORT marks the word connecting the ARG1 and the PRED.
+It is guaranteed that there is one and only one ARG1 in each sentence of the dataset.
 

### 2022-05-04 src/paper.tex
Update

@@
 In this paper, we select features including the word stem, the neighboring 2 words, POS tags, NG-BIO tags, whether capitalized and the position of the word in the sentence.
+Figure \ref{fig:maxent-feature-sample} shows the features we selected for the maximum entropy baseline.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{assets/maxent-feature-sample.png}
+  \caption{Sample sentence features for maxent system}
+  \label{fig:maxent-feature-sample}
+\end{figure}
 
@@
 By locating the token on the original input token list with the start index and end index, we can reconstruct the ARG1 label of the sentence.
+The answer relocation is a bit more complicated due to the tokenization discrepancies between the original input and the tokenized input.
+This is explained in detailed in section \ref{section:data-preprocessing}.
 
@@
 It is guaranteed that there is one and only one ARG1 in each sentence of the dataset.
+
+\subsection{Data Preprocessing}
+\label{section:data-preprocessing}
+
+Even though for deep neural network input wouldn't need much feature engineering, we still need to tokenize the text and convert the text into numerical representation so that it can be served as the input of the model.
+For DistilBERT-based pipelines, the tokenizer provided by DistilBERT is used to tokenize the text.
+However, the dataset is already tokenized and the way DistilBERT tokenizes a sentence could be different from how the sentences are already tokenized in the dataset.
+More specifically, the tokenizer from DistilBERT could tokenize the sentence into even smaller tokens than the tokenizer used in the dataset.
+Therefore, this could cause the output label of the model fail to align with the input given.
+Fortunately, the results of the DistilBERT tokenizer include the align information for the tokenization.
+With this information, we can reconstruct the tokenized sentence from the DistilBERT tokenizer output and match the model output with the original input.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{assets/dataset-one-qa-sample.png}
+  \caption{One sample sentence for QA task}
+  \label{fig:dataset-one-qa-sample}
+\end{figure}
+
+A special treatment for the question-answering pipeline is that the ARG1 label has to be transformed into the answer location (the start and end indexes).
+And the question prompt for every sample is the same "What is the ARG1 of the sentence?".
+The same question prompt is used for validation and testing.
+Figure \ref{fig:dataset-one-qa-sample} is one processed sample sentence for the QA task, inputs are padded in batched and stacked as matrix to be able to be processed by the model in batches.
+\verb|input_ids| are the numerized tokens of both the question prompt and the input text concatenated by \verb|102|.
+\verb|attention_mask| is the attention the model should be given to the tokens, \verb|0| means the token should not be considered by the model.
+\verb|start_position| and \verb|end_position| are the start and end indexes of the answer in the input text.
+
+\subsection{Experiment Settings}
+
+All deep models used in this paper are implemented in PyTorch and with HuggingFace transformers libraries.
+The pre-trained models are fine-tuned on a single NVIDIA P100 (16GB) GPU on the Google Colab platform.
+The deep models are fine-tuned for 10 epochs with the learning rate of \verb|2e-5| and weight decay of \verb|0.01|.
+For token classification tasks, the batch size is 64.
+For question-answering tasks, the input would be bigger with the question prompt, so the batch size is set to 32 to be able to fit into the GPU's RAM.
 

### 2022-05-04 src/paper.tex
Update

@@
 And the question prompt for every sample is the same "What is the ARG1 of the sentence?".
-The same question prompt is used for validation and testing.
-Figure \ref{fig:dataset-one-qa-sample} is one processed sample sentence for the QA task, inputs are padded in batched and stacked as matrix to be able to be processed by the model in batches.
+The exact same question prompt is used for validation and testing.
+Figure \ref{fig:dataset-one-qa-sample} is one processed sample sentence for the QA task, inputs are padded in batch and stacked as matrix to be able to be processed by the model in batches.
 \verb|input_ids| are the numerized tokens of both the question prompt and the input text concatenated by \verb|102|.
@@
 For question-answering tasks, the input would be bigger with the question prompt, so the batch size is set to 32 to be able to fit into the GPU's RAM.
+
+\subsection{Evaluation Metrics}
+
+To evaluate the performance of the model, we used precision, recall and F1-score as evaluation metrics.
+The precision and recall are calculated by the number of correct predictions divided by the total number of predictions.
+The F1-score is calculated by the harmonic mean of precision and recall.
+Below are the formulas for calculating the precision, recall and F1-score, in which TP is the number of true positives, FP is the number of false positives, FP is the number of false positives and FN is the number of false negatives.
+
+\begin{equation}
+  Precision={TP\over{TP+FP}}
+\end{equation}
+
+\begin{equation}
+  Recall={TP\over{TP+FN}}
+\end{equation}
+
+\begin{equation}
+  F1={2\times{Precision}\times{Recall}\over{Precision+Recall}}
+\end{equation}
 

### 2022-05-04 src/paper.tex
Update

@@
 
+\subsection{Partitive Dataset}
+
+Apart from the original \% task, we also experimented the token classification of DistilBERT on the combined dataset of \% and partitive datasets of NomBank.
+Different from the \% dataset, there's not only ARG1 but also ARG0, ARG2...
+and more role labels in the partitive dataset.
+In order to adopt the same pipelines, we preprocessed the partitive dataset into the same format as the \% dataset and combine them together into a larger dataset.
+The larger dataset is also split into training, dev and test set.
+The training set has 12991 sentences or 380247 words, the dev set has 426 sentences or 12671 words, and the test set has 746 sentences or 21536 words.
+
 \section*{Acknowledgements}

### 2022-05-04 src/paper.tex
Update

@@
 \begin{abstract}
-  This document is a supplement to the general instructions for *ACL authors. It contains instructions for using the \LaTeX{} style files for ACL conferences.
-  The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
-  These instructions should be used both for papers submitted for review and for final versions of accepted papers.
+  This paper presents our attempts of multiple pipelines to find ARG1 of partitive nouns in NomBank with DistilBERT.
+NomBank is an annotation project at New York University based on Penn Treebank II corpus.
+Finding ARG1 of partitive nouns in the databank is an semantic role labeling (SRL) problem, which here we treated as a token classification task or a question-answering task.
+We adopted a knowledge-distilled version of BERT, DistilBERT, into our SRL pipeline, leveraging the knowledge of English Wikipedia and Toronto Book Corpus that the model was originally trained on.
+For the \% dataset, we achieved an F1 score of 0.9267 on the test set.
+And for the partitive dataset, we achieved an F1 score of 0.7945 on the test set.
 \end{abstract}
@@
 
-More recently, the NLP community has seen huge popularity in heavily adopting pretraining-based langauge models.
+More recently, the NLP community has seen huge popularity in heavily adopting pretraining-based langauge models in attempt to transfer knowledge learned from large corpus into more specific tasks.
 BERT (Devlin et al., 2018) is a large-size language representation model trained on a large corpus of English text that can achieve state-of-the-art results on a variety of natural language processing tasks.
@@
 
-This paper presents a token classification approach using pre-trained DistilBERT to find ARG1 of partitive nouns in NomBank.
+This paper presents multiple token classification approaches using pre-trained DistilBERT to find ARG1 of partitive nouns in NomBank.
 It focuses on partitive nouns (nouns that are used to describe a part or quantity of something) and the partitive task.
@@
 
-In addition to the token classification approach above, this paper also experiments with question-answer task, transforming the original ARG1 finding task into the task of make the model answer the question "What is the ARG1 of this sentence?".
+In addition to the token classification approaches above, this paper also experiments with question-answer task, transforming the original ARG1 finding task into the task of make the model answer the question "What is the ARG1 of this sentence?".
 The advantage of this adaptation is that the model would stably output exactly one ARG1 for each sentence whereas token classification could give each sentence 0 to N ARG1s.
@@
 BERT, or Bidirectional Encoder Representations from Transformers (Devlin et al., 2018), has shown state-of-the-art results on many NLP tasks.
+The BERT base model has 110 million trainable parameters and was trained on a concentration of English Wikipedia and Toronto Book Corpus.
 There have been many attempts to compress BERT into a smaller model, among which DistilBERT (Sanh et al., 2019) successfully reduces the size of a BERT model by 40\%, while retaining 97\% of its language understanding capabilities and being 60\% faster, leveraging  knowledge distillation (Bucila et al., 2006, Hinton et al., 2015) during the pre-training phase.
@@
 
+However, the NomBank dataset provisions text as already tokenized.
+The way the tokenizer provided by DistilBERT is often more fine-grained than how the NomBank dataset provides the text, causing some aligning issues.
+We fix this by align the tokens using \verb|word_ids| in the tokenization output.
+This is explained in detailed in section \ref{section:data-preprocessing}.
+
 \begin{figure}[h]
@@
 \end{figure}
+
+In practice, this pipeline has the tendency of over predicting ARG1 labels.
+It predicts on a per-token basis, making classification of whether the token is an ARG1 or not on every token, thus possibly producing 0 to multiple ARG1s in one sentence.
+It is shown by our experiments that the deep models are more common to produce more than 1 ARG1s in one sentence.
+The ground truth, however, is one and only one ARG1 per sentence.
+A treatment of this inconsistency is to always force one ARG1 by the logits output of the deep neural network.
+We assign the token with the largest logit value in the output vector for the whole sentence to be the ARG1.
 
@@
 The answer relocation is a bit more complicated due to the tokenization discrepancies between the original input and the tokenized input.
-This is explained in detailed in section \ref{section:data-preprocessing}.
+Again, this is explained in detailed in section \ref{section:data-preprocessing}.
 
@@
 
-\section*{Acknowledgements}
+\section{Experiment Results}
+
+\begin{table*}
+  \centering
+  \begin{tabular}{c||c|c|c}
+    \hline
+    \textbf{Model}        & \textbf{Precision} & \textbf{Recall} & \textbf{F1-Score} \\
+    \hline
+    MaxEnt Baseline       & {71.88\%}          & {61.33\%}       & {66.19\%}         \\
+    DistilBERT            & {93.75\%}          & {90.00\%}       & {91.84\%}         \\
+    DistilBERT (POS+BIO)  & {93.19\%}          & {91.33\%}       & {92.25\%}         \\
+    DistilBERT (QA)       & {92.00\%}          & {92.00\%}       & {92.00\%}         \\
+    DistilBERT (ONE ARG1) & {92.67\%}          & {92.67\%}       & {92.67\%}         \\
+    \hline
+  \end{tabular}
+  \caption{Precision, Recall and F1-Score on the \% dataset}
+  \label{tab:results-on-first-dataset}
+\end{table*}
+
+\begin{table*}
+  \centering
+  \begin{tabular}{c||c|c|c}
+    \hline
+    \textbf{Model}  & \textbf{Precision} & \textbf{Recall} & \textbf{F1-Score} \\
+    \hline
+    MaxEnt Baseline & {55.33\%}          & {36.02\%}       & {43.64\%}         \\
+    DistilBERT      & {80.49\%}          & {78.43\%}       & {79.45\%}         \\
+    \hline
+  \end{tabular}
+  \caption{Precision, Recall and F1-Score on the partitive dataset}
+  \label{tab:results-on-partitive-dataset}
+\end{table*}
+
+\section{Conclusion}
+
+\section{Future Work}
+
+\section*{References}
 
@@
 
-\appendix
-
-\section{Example Appendix}
-\label{sec:appendix}
-
-This is an appendix.
-
 \end{document}

### 2022-05-04 src/paper.tex
Update

@@
 
+The partitive dataset, in comparison with the \% dataset, has more distractions in terms of ARG1 finding task since ARG0, ARG2 and other labels are given.
+Also, there could be more than one or zero ARG1s in one sentence, thus making our QA and ONE ARG1 pipelines useless since the tendency of producing only one ARG1 is no longer preferred.
+
 \section{Experiment Results}
@@
     DistilBERT           & {80.49\%}          & {78.43\%}       & {79.45\%}         \\
+    DistilBERT (POS+BIO) & {81.53\%}          & {76.94\%}       & {79.16\%}         \\
     \hline
@@
 \end{table*}
+
+We experimented with multiple ARG1 finding models and pipelines on both \% dataset and partitive dataset from the NomBank corpus.
+The results are shown in Table \ref{tab:results-on-first-dataset} and Table \ref{tab:results-on-partitive-dataset} respectively.
+
+For the partitive dataset, because there could be zero or multiple ARG1s in one sentence for ground truth, there's no need to force model to predict only one ARG1, thus we abandoned the QA and ONE ARG1 pipelines for the partitive dataset.
+
+As shown by Table \ref{tab:results-on-first-dataset}, the MaxEnt baseline achieved an F1 score of \verb|0.6619|.
+The DistilBERT models perform much better than the MaxEnt Baseline model on the \% dataset generally even when given less features, achieving an F1 score of 0.9184 for the basic pipeline,  \verb|0.9225| for the feature-enhanced pipeline,  \verb|0.92| for the QA pipeline and  \verb|0.9267| for the ONE ARG1 pipeline.
+The performance differences between different DistilBERT-based pipelines, however, are not significant.
+POS tags and NG-BIO tags likely don't have much effect on the performance of the model.
+
+As for the partitive dataset, it is also shown by Table \ref{tab:results-on-partitive-dataset} that the DistilBERT model performs better than the MaxEnt Baseline model that achieved an F1 score of  \verb|0.4364|.
+The basic pipeline achieved an F1 score of  \verb|0.7945|.
+It is also observed that the POS tags and NG-BIO tags features didn't have significant impact on the performance of the model, achieving an F1 score of only  \verb|0.7916|.
 

### 2022-05-05 src/paper.tex
Update

@@
 % Standard package includes
+\usepackage{lastpage}
+\usepackage{fancyhdr}
 \usepackage{times}
@@
 
+\pagestyle{fancy}
+\fancyhead{}
+\renewcommand{\headrulewidth}{0pt}
+\fancyfoot[C]{Page \thepage \hspace{1pt} of \pageref{LastPage}}
+
 % If the title and author information does not fit in the area allocated, uncomment the following
@@
 %         Author n \\ Address line \\ ... \\ Address line}
-% To start a seperate ``row'' of authors use \AND, as in
+% To start a separate ``row'' of authors use \AND, as in
 % \author{Author 1 \\ Address line \\  ... \\ Address line
@@
 
-More recently, the NLP community has seen huge popularity in heavily adopting pretraining-based langauge models in attempt to transfer knowledge learned from large corpus into more specific tasks.
+More recently, the NLP community has seen huge popularity in heavily adopting pretraining-based language models in attempt to transfer knowledge learned from large corpus into more specific tasks.
 BERT (Devlin et al., 2018) is a large-size language representation model trained on a large corpus of English text that can achieve state-of-the-art results on a variety of natural language processing tasks.
@@
 
-In addition to the token classification approaches above, this paper also experiments with question-answer task, transforming the original ARG1 finding task into the task of make the model answer the question "What is the ARG1 of this sentence?".
+In addition to the token classification approaches above, this paper also experiments with question-answer task, reframing the original ARG1 finding task into the task of make the model answer the question "What is the ARG1 of this sentence?".
 The advantage of this adaptation is that the model would stably output exactly one ARG1 for each sentence whereas token classification could give each sentence 0 to N ARG1s.
@@
 \section{ARG1 Finding Pipelines}
+
+We developed several pipelines for finding ARG1 of partitive nouns in NomBank. One pipeline utilizes maximum entropy classifiers, the others utilizes the pre-trained DistilBERT model.
 
@@
 
-In practice, this pipeline has the tendency of over predicting ARG1 labels.
+In practice, this pipeline has the tendency of over generating ARG1 labels.
 It predicts on a per-token basis, making classification of whether the token is an ARG1 or not on every token, thus possibly producing 0 to multiple ARG1s in one sentence.
@@
 In a sentence in the \% dataset, the PRED labels \% symbol, the ARG1 is the partitive noun that \% symbol refers to, and the SUPPORT marks the word connecting the ARG1 and the PRED.
-It is guaranteed that there is one and only one ARG1 in each sentence of the dataset.
+It is guaranteed that there is one and only one ARG1 in each sentence of the \% dataset.
 
@@
 The pre-trained models are fine-tuned on a single NVIDIA P100 (16GB) GPU on the Google Colab platform.
+The baseline maximum entropy classifier implementation we used is \verb|opennlp.maxent| by Baldridge et al.
 The deep models are fine-tuned for 10 epochs with the learning rate of \verb|2e-5| and weight decay of \verb|0.01|.
@@
 
-\section{Experiment Results}
-
 \begin{table*}
@@
 
-\begin{table*}
+\begin{table*}[t]
   \centering
@@
 
+\section{Experiment Results}
+
 We experimented with multiple ARG1 finding models and pipelines on both \% dataset and partitive dataset from the NomBank corpus.
@@
 
+\subsection{\% Dataset}
+\label{sec:results-first-dataset}
+
 As shown by Table \ref{tab:results-on-first-dataset}, the MaxEnt baseline achieved an F1 score of \verb|0.6619|.
 The DistilBERT models perform much better than the MaxEnt Baseline model on the \% dataset generally even when given less features, achieving an F1 score of 0.9184 for the basic pipeline,  \verb|0.9225| for the feature-enhanced pipeline,  \verb|0.92| for the QA pipeline and  \verb|0.9267| for the ONE ARG1 pipeline.
-The performance differences between different DistilBERT-based pipelines, however, are not significant.
-POS tags and NG-BIO tags likely don't have much effect on the performance of the model.
+However, The performance differences between different DistilBERT-based pipelines are very minor and can possibly be counted as experimental error.
+The introduction of additional POS tags and NG-BIO tags features likely don't seem to improve the model's performance in any statistically significant way.
+
+A major advantage of DistilBERT pipelines over the baseline is the limited number of features needed.
+The basic and the QA pipelines only require the text input itself and feature-enhanced one requires the text input, the POS tags and the NG-BIO tags.
+
+By a closer look to where the model struggles to produce correct predictions, Figure \ref{fig:prediction-one-sample} being one of the examples, we can see that the model is trying to predict more than one ARG1s in the sentence.
+In the given example, the ground truth is only \verb|tons| and the model is trying to predict \verb|tons| and also \verb|steel|.
+Though being over generating ARG1s, this is actually a very sensible prediction since "tons of steel" is indeed a noun group that the \% symbol is referring to.
+And our solutions to this over generating problem (QA task and forcing one ARG1) didn't quite improve the performance.
+In our experiment, we found that, when faced with multiple ARG1 candidates in a noun group, the model tends to choose the head noun as the ARG1, which in this case is \verb|steel| instead of the ground truth \verb|tons|.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{assets/prediction-one-sample.png}
+  \caption{One over-generating prediction sample for DistilBERT}
+  \label{fig:prediction-one-sample}
+\end{figure}
+
+\subsection{Partitive Dataset}
 
@@
 The basic pipeline achieved an F1 score of  \verb|0.7945|.
-It is also observed that the POS tags and NG-BIO tags features didn't have significant impact on the performance of the model, achieving an F1 score of only  \verb|0.7916|.
+It is also observed that the POS tags and NG-BIO tags features didn't have statistically significant improvement on the performance of the model, achieving an F1 score of only \verb|0.7916|.
+When compared to the \% dataset, the decrease in performance is expected since the partitive dataset has more distractions and noise.
+The tendency of over generating ARG1s is also observed for DistilBERT models in the partitive dataset, and can not easily be improved by forcing one ARG1, which is consistent with the observations made for the result on \% dataset shown in \ref{sec:results-first-dataset}.
 
@@
 
-\section{Future Work}
+This paper has discussed the semantic role labeling task of finding ARG1 of partitive nouns in NomBank.
+And we have experimented with multiple ARG1 finding models and pipelines on \% dataset and partitive dataset from the NomBank corpus, taking advantages of the state-of-the-art DistilBERT model, then successfully developed a SRL system that can achieve an F1 score of \verb|0.9267| on the test set of the \% dataset and an F1 score of \verb|0.7945| on combined dataset of both \% dataset and partitive dataset.
+In comparisons with the baseline model, pre-trained DistilBERT models have shown their great advantage of text representation in this specific NLP task.
+
+By the results of our experiments on feature-enhanced pipelines, we also show that the DistilBERT model cannot be significantly improved by adding POS tags and NG-BIO tags features.
+This is consistently shown by our experiments on both \% dataset and partitive dataset.
+Besides, for the \% dataset, question-answering variant and forcing one ARG1 variant of DistilBERT models have not shown much significant improvement on the performance of the model either.
+However, the QA approach is indeed a novel perspective to look at the task of finding ARG1, reframing a SRL task into a QA task which is a more open and flexible task.
+The flexibility comes with the free choice of prompt question - a prompt question can be any text.
+Therefore, what could possibly be further investigated is the question prompt we use to ask the model to find ARG1.
+
+\section{Discussion and Future Work}
 
 \section*{References}
-
-This document has been adapted
-by Steven Bethard, Ryan Cotterell and Rui Yan
-from the instructions for earlier ACL and NAACL proceedings, including those for
-ACL 2019 by Douwe Kiela and Ivan Vuli\'{c},
-NAACL 2019 by Stephanie Lukin and Alla Roskovskaya,
-ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu,
-NAACL 2018 by Margaret Mitchell and Stephanie Lukin,
-Bib\TeX{} suggestions for (NA)ACL 2017/2018 from Jason Eisner,
-ACL 2017 by Dan Gildea and Min-Yen Kan,
-NAACL 2017 by Margaret Mitchell,
-ACL 2012 by Maggie Li and Michael White,
-ACL 2010 by Jing-Shin Chang and Philipp Koehn,
-ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui,
-ACL 2005 by Hwee Tou Ng and Kemal Oflazer,
-ACL 2002 by Eugene Charniak and Dekang Lin,
-and earlier ACL and EACL formats written by several people, including
-John Chen, Henry S. Thompson and Donald Walker.
-Additional elements were taken from the formatting instructions of the \emph{International Joint Conference on Artificial Intelligence} and the \emph{Conference on Computer Vision and Pattern Recognition}.
 

### 2022-05-05 src/paper.tex
Update

@@
 
-As for the partitive dataset, it is also shown by Table \ref{tab:results-on-partitive-dataset} that the DistilBERT model performs better than the MaxEnt Baseline model that achieved an F1 score of \verb|0.4364|.
-The basic pipeline achieved an F1 score of  \verb|0.7945|.
+As for the partitive dataset, it is also shown by Table \ref{tab:results-on-partitive-dataset} that the DistilBERT model performs better than the MaxEnt Baseline model which achieved an F1 score of \verb|0.4364|.
+The basic DistilBERT pipeline achieved an F1 score of  \verb|0.7945|.
 It is also observed that the POS tags and NG-BIO tags features didn't have statistically significant improvement on the performance of the model, achieving an F1 score of only \verb|0.7916|.
-When compared to the \% dataset, the decrease in performance is expected since the partitive dataset has more distractions and noise.
+Aside from that, when compared to the \% dataset, the decrease in performance is expected since the partitive dataset has more distractions and noise.
 The tendency of over generating ARG1s is also observed for DistilBERT models in the partitive dataset, and can not easily be improved by forcing one ARG1, which is consistent with the observations made for the result on \% dataset shown in \ref{sec:results-first-dataset}.
@@
 
+Based on the performance decrease observed in the partitive dataset, we also concluded that the ARG1 finding pipelines are generally sensitive to the noise in the partitive dataset.
+However, the DistilBERT models are relatively more robust to noise with 14.26\% decrease in performance compared to the baseline MaxEnt model's 34.06\% decrease.
+
 \section{Discussion and Future Work}

### 2022-05-05 src/paper.tex
Update

@@
 % Standard package includes
+\usepackage{natbib}
 \usepackage{lastpage}
@@
 
-\section*{References}
+The two extra POS tags and NG-BIO tags features didn't seem to improve the performance of the model in a statistically significant way.
+This could be due to the huge amount of knowledge the deep model has already gained from the pre-training stage, thus rendering the addition of these two features insignificant.
+However, feature engineering in general could possibly be helpful in improving the model.
+We could investigate more selections of features and try to incorporate them into the pipelines we have developed.
+The features that are not covered by the pre-trained DistilBERT models could help the model in the task of finding ARG1.
+
+Question-answering pipeline is a novel approach to the task of finding ARG1 of partitive nouns in NomBank.
+As mentioned, what we haven't explored enough on is the question prompt we use to ask the model to find ARG1.
+The question prompt can be any text, but the way we framed the question could be the key to how well the model would comprehend the task and execute it.
+For future work, we'd like to explore more kinds of question prompts and analyze the effect of different question prompts on the performance of the model.
+
+The system we developed has shown good performance on the \% dataset.
+However, in real-world applications, like shown on the partitive dataset, the noise could majorly impact the performance of the model.
+The directions of reducing the impact of noise could be exploring preprocessing techniques in attempt to remove the noise, or architectural changes in the model to make it more robust to noise.
+A plausible idea is to use BERT output as an embedding of the token, then feed it with other feature to an RNN model to predict the ARG1.
+More trainable layers for the token classification task could make the model more robust to noise.
+
+% \printbibliography
 
 % Entries for the entire Anthology, followed by custom entries
-\bibliography{anthology,custom}
-\bibliographystyle{acl_natbib}
+\bibliographystyle{plain}
+\bibliography{refs}
 

### 2022-05-05 src/paper.tex
Update

@@
 
-NomBank (Meyers et al., 2004c) is a databank project at New York University that adds annotation layer of argument structure for instances in the Penn Treebank II corpus.
+NomBank (Meyers et al., 2004c) is a databank project at New York University that adds annotation layer of argument structure for instances in the Penn Treebank II corpus \cite{meyers2004nombank}.
 Apart from the more commonly researched nominalizations of verbs and nominalizations of adjectives, it also covers relational nouns, partitive nouns and several other types of argument-taking nouns.
@@
 More recently, the NLP community has seen huge popularity in heavily adopting pretraining-based language models in attempt to transfer knowledge learned from large corpus into more specific tasks.
-BERT (Devlin et al., 2018) is a large-size language representation model trained on a large corpus of English text that can achieve state-of-the-art results on a variety of natural language processing tasks.
+BERT (Devlin et al., 2018) is a large-size language representation model trained on a large corpus of English text that can achieve state-of-the-art results on a variety of natural language processing tasks \cite{devlin2018bert}.
 BERT came a decade later than the release of NomBank and there's been little previous work using it to conduct NomBank-based tasks and related experiments.
 However, as powerful as BERT is, its large parameters size makes it significantly more computationally expensive to train and use.
-On the other hand, DistilBERT is a distilled student model of BERT that retains 97\% of BERT's language understanding capabilities while being 40\% smaller and 60\% faster.
+On the other hand, DistilBERT is a distilled student model of BERT that retains 97\% of BERT's language understanding capabilities while being 40\% smaller and 60\% faster \cite{sanh2019distilbert}.
 This makes it a great candidate to train when facing with limited resources.
@@
 
-NomBank (Meyers et al., 2004c), as a databank extending the frames of NOMLEX and PropBank, annotates argument structures of common nouns similar to how PropBank annotates predicating verbs.
+NomBank (Meyers et al., 2004c), as a databank extending the frames of NOMLEX and PropBank, annotates argument structures of common nouns similar to how PropBank annotates predicating verbs \cite{meyers2004nombank}.
 The development of the NomBank corpus has made several other work on argument structure extraction more accessible.
-Jiang and Ng (2006) attempts the first NomBank-based automatic semantic role labeling system after the databank's release.
-Ping (2006)  adapts a PropBank-based SRL system to the SRL task of NomBank, achieving an overall F1 score of 72.73 on section 23 of the NomBank corpus.
+Jiang and Ng (2006) attempts the first NomBank-based automatic semantic role labeling system after the databank's release \cite{jiang2006semantic}.
+Ping (2006) adapts a PropBank-based SRL system to the SRL task of NomBank, achieving an overall F1 score of 72.73 on section 23 of the NomBank corpus \cite{ping2006investigations}.
 
-BERT, or Bidirectional Encoder Representations from Transformers (Devlin et al., 2018), has shown state-of-the-art results on many NLP tasks.
+BERT, or Bidirectional Encoder Representations from Transformers (Devlin et al., 2018), has shown state-of-the-art results on many NLP tasks \cite{devlin2018bert}.
 The BERT base model has 110 million trainable parameters and was trained on a concentration of English Wikipedia and Toronto Book Corpus.
-There have been many attempts to compress BERT into a smaller model, among which DistilBERT (Sanh et al., 2019) successfully reduces the size of a BERT model by 40\%, while retaining 97\% of its language understanding capabilities and being 60\% faster, leveraging  knowledge distillation (Bucila et al., 2006, Hinton et al., 2015) during the pre-training phase.
+There have been many attempts to compress BERT into a smaller model, among which DistilBERT (Sanh et al., 2019) successfully reduces the size of a BERT model by 40\%, while retaining 97\% of its language understanding capabilities and being 60\% faster \cite{sanh2019distilbert}, leveraging  knowledge distillation (Bucila et al., 2006, Hinton et al., 2015) during the pre-training phase \cite{bucilua2006model,hinton2015distilling}.
 
-More recent development on semantic role labeling (SRL) has shifted from feature engineering to architecture-based modeling leveraging deep neural networks (Collobert
-et al., 2011).
-Several recent notable approaches suggest only using raw tokenized text as input and let the model learn the features from the text itself (He et al., 2017; Sahin and Steedman, 2018; Marcheggiani et al., 2017; Strubell et al., 2018).
+More recent development on semantic role labeling (SRL) has shifted from feature engineering to architecture-based modeling leveraging deep neural networks (Collobert et al., 2011) \cite{collobert2011natural}.
+Several recent notable approaches suggest only using raw tokenized text as input and let the model learn the features from the text itself (He et al., 2017; Sahin and Steedman, 2018; Marcheggiani et al., 2017; Strubell et al., 2018) \cite{he2017deep,csahin2018character,marcheggiani2017encoding,strubell2018linguistically}.
 This end-to-end approach allows the model to easily generalize from one SRL task to another without very task-specific feature engineering effort.
@@
 The baseline we use is a maximum entropy machine learning method in a token-by-token classification manner.
-Maximum entropy is a general technique for estimating probability distributions from data.
+Maximum entropy is a general technique for estimating probability distributions from data \cite{berger1996maximum}.
 Labeled training data
@@
 
-All deep models used in this paper are implemented in PyTorch and with HuggingFace transformers libraries.
+All deep models used in this paper are implemented in PyTorch and with HuggingFace transformers libraries \cite{wolf2019huggingface}.
 The pre-trained models are fine-tuned on a single NVIDIA P100 (16GB) GPU on the Google Colab platform.
@@
 % \printbibliography
-
-% Entries for the entire Anthology, followed by custom entries
 \bibliographystyle{plain}

### 2022-05-07 submissions/pack.sh
Update my submissions

@@ -1,0 +1,1 @@
+zip -r submission.zip paper.pdf source
